\bf Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-04-25 doc/paper.Rmd
three more points for CS1

\hh{don't split the discussion on the size. between the next paragraph and }
<!--The majority of Bullet profiles and signatures of the Hamby study \citep{hamby} used in this paper are extracted by procedures mentioned by  \citet{aoas}.--> 
There are two sources of scans for sets from the Hamby study available to us: scans of Hamby 44 and Hamby 252 are available from the NIST database \citep{nist}. Hamby 44 has also been made available to us and has been scanned locally for CSAFE at the Roy J.\ Carver High Resolution Microscopy Facility using a Sensofar confocal light microscope. 
Scans in the NIST database are made with a NanoFocus at 20x magnification. The resolutions of the two instruments are different: the NIST scans are taken at a resolution of 1.5625 $\mu m$ per pixel, while the CSAFE scans are available at a resolution of  0.645 $\mu m$ per pixel.
The length of an average bullet land from Hamby (9 mm Ruger P85) is about 2 millimeter, resulting in signatures of about 1200 pixels for NIST scans, and about 3000 pixels for CSAFE scans.

@@

## A problem with failures and modification

Looking closer at \autoref{eq.start}, we see that by definition, some number of tests will fail to produce a result, either because the number of eligible same-shift pairs is zero, or the number of different-shift opairs is zero. \hh{XXX The problem of failed tests is first mentioned in XXX}

@@

@@

```{r sigs-profiles, fig.width = 8, fig.height = 2.5, fig.cap="Bullet land profile (left) and the corresponding signature (right) for one of the lands of Hamby-44."}
p1 <- sigs_graphics[[1]] %>% filter(land_id==19) %>%
  ggplot(aes(x = y/1000, y = value)) + geom_line() +
  theme_bw() +
  ylab(expression(paste("Depth (in ",mu,m,")", sep=""))) + 
  xlab(expression(paste("Relative location (in mm)", sep=""))) + 
  ggtitle("Profile")

@@

profiles <- tidyr::gather(profile, coarseness, values, lw10:lw30)
profiles <- profiles %>% mutate(
  c = readr::parse_number(coarseness)/100
)
p1 <- profiles %>% 
  ggplot(aes(x = y, y = value-values)) + geom_line() +
  theme_bw() +
  ylab(expression(paste("Depth (in ",mu,m,")", sep=""))) + 
  xlab(expression(paste("Relative Location (in ",mu,m,")", sep=""))) +
  facet_grid(~c, labeller="label_both")

>>>>

There are two sources of scans for sets from the Hamby study available to us: scans of Hamby 44 and Hamby 252 are available from the NIST database \citep{nist}. Hamby 44 has also been made available to us and has been scanned locally for CSAFE at the Roy J.\ Carver High Resolution Microscopy Facility using a Sensofar confocal light microscope. 
Scans in the NIST database are made with a NanoFocus at 20x magnification. The resolutions of the two instruments are different: the NIST scans are taken at a resolution of 1.5625 $\mu m$ per pixel, while the CSAFE scans are available at a resolution of  0.645 $\mu m$ per pixel.
The length of an average bullet land from Hamby (9 mm Ruger P85) is about 2 millimeter, resulting in signatures of about 1200 pixels for NIST scans, and about 3000 pixels for CSAFE scans.

@@

## A problem with failed tests

Looking closer at \autoref{eq.start}, we see that by definition, some number of tests will fail to produce a result. \hh{The problem of failed tests is first mentioned in \citet{afte-chumbley}. Unfortunately, the authors do not provide any percentage of how many tests failed for their data.}
The algorithm fails to produce for two reasons: either the number of eligible same-shift pairs is zero, or the number of different-shift pairs is zero.

@@

## A modified approach

@@

```{r sigs-profiles, fig.width = 8, fig.height = 2.5, fig.cap="Bullet land profile (left) and the corresponding signature (right) for one of the lands of Hamby-44."}
p1 <- sigs_graphics[[1]] %>% filter(land_id==19) %>%
  ggplot(aes(x = y, y = value)) + geom_line() +
  theme_bw() +
  ylab(expression(paste("Depth (in ",mu,m,")", sep=""))) + 
  xlab(expression(paste("Relative location (in ",mu,m,")", sep=""))) + 
  ggtitle("Profile")

@@

profiles <- tidyr::gather(profile, coarseness, values, lw10:lw30)
profiles <- profiles %>% mutate(
  c = readr::parse_number(coarseness)/100
)
p1 <- profiles %>% 
  ggplot(aes(x = y/1000, y = value-values)) + geom_line() +
  theme_bw() +
  ylab(expression(paste("Depth (in ",mu,m,")", sep=""))) + 
  xlab(expression(paste("Relative Location (in mm)", sep=""))) +
  facet_grid(~c, labeller="label_both")

### 2018-04-25 doc/paper.tex
three more points for CS1

\hh{don't split the discussion on the size. between the next paragraph and }
There are two sources of scans for sets from the Hamby study available
to us: scans of Hamby 44 and Hamby 252 are available from the NIST
database \citep{nist}. Hamby 44 has also been made available to us and
has been scanned locally for CSAFE at the Roy J.~Carver High Resolution
Microscopy Facility using a Sensofar confocal light microscope. Scans in
the NIST database are made with a NanoFocus at 20x magnification. The
resolutions of the two instruments are different: the NIST scans are
taken at a resolution of 1.5625 \(\mu m\) per pixel, while the CSAFE
scans are available at a resolution of 0.645 \(\mu m\) per pixel. The
length of an average bullet land from Hamby (9 mm Ruger P85) is about 2
millimeter, resulting in signatures of about 1200 pixels for NIST scans,
and about 3000 pixels for CSAFE scans.

@@

\subsection{A problem with failures and
modification}\label{a-problem-with-failures-and-modification}

Looking closer at \autoref{eq.start}, we see that by definition, some
number of tests will fail to produce a result, either because the number
of eligible same-shift pairs is zero, or the number of different-shift
opairs is zero.
\hh{XXX The problem of failed tests is first mentioned in XXX}

@@

>>>>

There are two sources of scans for sets from the Hamby study available
to us: scans of Hamby 44 and Hamby 252 are available from the NIST
database \citep{nist}. Hamby 44 has also been made available to us and
has been scanned locally for CSAFE at the Roy J.~Carver High Resolution
Microscopy Facility using a Sensofar confocal light microscope. Scans in
the NIST database are made with a NanoFocus at 20x magnification. The
resolutions of the two instruments are different: the NIST scans are
taken at a resolution of 1.5625 \(\mu m\) per pixel, while the CSAFE
scans are available at a resolution of 0.645 \(\mu m\) per pixel. The
length of an average bullet land from Hamby (9 mm Ruger P85) is about 2
millimeter, resulting in signatures of about 1200 pixels for NIST scans,
and about 3000 pixels for CSAFE scans.

@@

\subsection{A problem with failed
tests}\label{a-problem-with-failed-tests}

Looking closer at \autoref{eq.start}, we see that by definition, some
number of tests will fail to produce a result.
\hh{The problem of failed tests is first mentioned in \citet{afte-chumbley}. Unfortunately, the authors do not provide any percentage of how many tests failed for their data.}
The algorithm fails to produce for two reasons: either the number of
eligible same-shift pairs is zero, or the number of different-shift
pairs is zero.

@@

\subsection{A modified approach}\label{a-modified-approach}
